Compare pseqs

### 2019-05-27 articletwo.Rmd
Wrong order
Minor

```{r odds htn lacto}
odds.hypertension.lactogroup <- glm.hypertension.lactogroup %>%
    filter(!grepl("Intercept", term)) %>%
    select(term, estimate, p.value, conf.low, conf.high) %>%
    add_row(term = "lacto_groups1", estimate = 1.0, conf.low = NA, conf.high = NA) %>%
    dplyr::filter(grepl("lacto", term))
odds.hypertension.lactogroup %>% kable
```

@@

>>>>

@@

Odds for hypertension

```{r odds htn lacto}
odds.hypertension.lactogroup <- glm.hypertension.lactogroup %>%
    broom::tidy(conf.int = TRUE, conf.level = 0.95, exponentiate = TRUE) %>%
    filter(!grepl("Intercept", term)) %>%
    select(term, estimate, p.value, conf.low, conf.high) %>%
    add_row(term = "lacto_groups1", estimate = 1.0, conf.low = NA, conf.high = NA) %>%
    dplyr::filter(grepl("lacto", term))
odds.hypertension.lactogroup %>% kable
```

### 2019-05-27 comparepseqs.Rmd
Minor

rds <- list("gtdb" = 1 , "centrifuge" = 2)
```

@@

    gs4 <- list(alpha.diversity.min$yaxis,
                alpha.diversity.min$plot,
                beta.diversity.min$plot,
                alpha.diversity.min$legend,
                alpha.diversity.min$xaxis,
                beta.diversity.min$xaxis,
                beta.diversity.min$xlab,
                text_grob(paste("A.", key), size = 18, just = "left"),
                alpha.diversity.full$yaxis,
                alpha.diversity.full$plot,
                beta.diversity.full$plot,  
                alpha.diversity.full$xaxis,
                beta.diversity.full$xaxis,
                beta.diversity.full$xlab,
                text_grob(paste("B.", key), size = 18, just = "left"))

@@

```{r plot alpha diversity, eval = FALSE}
g <- arrangeGrob(plotlist[[1]], plotlist[[2]], ncol=1)
ggsave(file="cache/plotlist.pdf", g, height=6*length(plotlist), width=10)
```

>>>>

rds <- list("gtdb" = 1 , "centrifuge" = 2, "ncbi" = 3)
```

@@

    gs4 <- list(alpha.diversity.min$yaxis,
                alpha.diversity.min$plot,
                beta.diversity.min$plot,
                alpha.diversity.min$legend,
                alpha.diversity.min$xaxis,
                beta.diversity.min$xaxis,
                beta.diversity.min$xlab,
                text_grob(sprintf("A. %s (%s)", key, paste(covariates.min, collapse = ", ")),
                          size = 16,
                          just = "left"),
                alpha.diversity.full$yaxis,
                alpha.diversity.full$plot,
                beta.diversity.full$plot,  
                alpha.diversity.full$xaxis,
                beta.diversity.full$xaxis,
                beta.diversity.full$xlab,
                text_grob(sprintf("B. %s (%s)", key, paste(covariates.full %>%
                                                           gsub("BL_USE_", "", .), collapse = ", ")),
                          size = 16, just = "left"))

@@

```{r plot alpha diversity, eval = FALSE}
g <- arrangeGrob(grobs = plotlist, ncol=2)
ggsave(file="cache/plotlist.pdf", g, height=6*length(plotlist)/1.5, width=10*2)
```
